\tname: A Database of Reproducible Bugs in Deep Learning Libraries to Enable Systematic Evaluation of Testing Techniques

### 2025-01-13 paper/main.tex
another pass

%%
%% The abstract is a short summary of the work to be presented in the
%% article.
\begin{abstract}
  \sloppy
  AI-enabled applications are prolific today. Deep Learning~(DL)
  libraries, such as \torch{} and \tf{}, provide the building
  blocks for the AI components of these applications. As any piece of
  software, these libraries can be buggy.
  %% and those bugs can affect a
  %% great deal of applications using those libraries.
  An impressive number of bug-finding techniques to address this
  problem have been proposed, but the lack of a curated set of
  reproducible bugs in DL libraries hinders credible evaluation of these
  techniques. We present \tname, a database of curated reproducible
  bugs to fill that gap.
  %% enable credible  evaluation of bug-finding DL library testing techniques.
  Our dataset currently consists of \numbugs{} environments to
  reproduce bugs across three popular DL libraries, namely, \jax,
  \tf, and \torch.
\textbf{Screencast}:~\url{https://tinyurl.com/BugsInDLLs}\\
\textbf{GitHub repository}:~\url{https://github.com/ncsu-swat/bugsindlls}    
\end{abstract}

@@

We present \tname, a database of curated reproducible bugs to
enable credible evaluation of DL library testing techniques. \tname\ is
equipped with a command-line interface to enable researchers to analyze
and reproduce bug instances.

@@

Tool execution proceeds in two steps: (1) Creation of Docker container
associated with a tool and (2) Execution of the tool.  The following
script executes the first step, i.e., it builds a Docker container for
FreeFuzz:

@@

\Fix{I am here -Marcelo}

Once the docker container is built and is running, providing the name of the container and the location of the script that can execute the tool (either absolute path or relative to the root of the repository) to the command "run-tool" in the framework along with the library and bug id will first reproduce the bug seperately and then update the environment inside the docker to run the tool with the script provided. For example, the issue no. 117033 and the \torch~library, the following command would run FreeFuzz on the enviroment of the bug:

@@

Initially the script reproduces the bug, then it updates the environment inside the docker container of FreeFuzz to match the enviroment of the bug. Then it proceeds to run the entire testing tool on the enviroment. After the execution completes, the output can be checked for all failures produced by FreeFuzz (saved inside the container) and manually inspected to see if any failure that can reveal the bug in question was generated by the tool. In this case, the failure generated by FreeFuzz could not generate a failure that can reveal this bug since the API "torch.\_dynamo.export" is not supported by FreeFuzz.

@@

@@

@@

\section{Research Methods}

>>>>

%%
%% The abstract is a short summary of the work to be presented in the
%% article.
\begin{abstract}
  \sloppy
  AI-enabled applications are prolific today. Deep Learning~(DL)
  libraries, such as \torch{} and \tf{}, provide the building
  blocks for the AI components of these applications. As any piece of
  software, these libraries can be buggy.
  %% and those bugs can affect a
  %% great deal of applications using those libraries.
  An impressive number of bug-finding techniques to address this
  problem have been proposed, but the lack of a curated set of
  reproducible bugs in DL libraries hinders credible evaluation of these
  techniques. We present \tname, a database of curated reproducible
  bugs to fill that gap.
  %% enable credible  evaluation of bug-finding DL library testing techniques.
  Our dataset currently consists of \numbugs{} environments to
  reproduce bugs across three popular DL libraries, namely, \jax,
  \tf, and \torch.
\end{abstract}

@@

We present \tname, a database of curated reproducible bugs to
enable credible evaluation of DL library testing techniques. \tname\ is
equipped with a command-line interface to enable researchers to analyze
and reproduce bug instances. The following screencast demonstrate some
of the features in \tname:

\url{https://tinyurl.com/BugsInDLLs}\\

\tname\ has been under active development since March 21, 2024, the
day of the first commit in the corresponding GitHub repository. Two
UROP students, two PhD students, and two faculty were involved in the
work. \tname\ is publicly available from the following URL:

\url{https://github.com/ncsu-swat/bugsindlls}

@@

Tool execution proceeds in two steps: (1) Creation of Docker container
associated with a tool and (2) Execution of the tool.  Let us
demonstrate this process on FreeFuzz~\cite{wei2022free}, an API-level
fuzzer for DL libraries. The following script executes the first step
of the two-step integration method.

%i.e., it builds a Docker container for FreeFuzz:

@@

\noindent
The script \CodeIn{install\_freefuzz\_docker.sh} contains the
following instructions:

\begin{lstlisting}[language=bash]
#!/bin/bash
git clone https://github.com/ise-uiuc/FreeFuzz.git
docker build -t freefuzz .
docker run --name freefuzz --gpus all -d freefuzz:latest
docker exec -it freefuzz mongorestore dump/
\end{lstlisting}

%\Fix{I am here -Marcelo}
%% Once the docker container is built and is running, providing the name
%% of the container and the location of the script that can execute the
%% tool (either absolute path or relative to the root of the repository)
%% to the command

The second step runs the \tname's command \CodeIn{run-tool}, which
proceeds in two steps (1) reproduce the bug separately, as done with
command \CodeIn{run-test}, and (2) then update the environment inside
the docker container of the tool to run the tool with the script
provided.\Fix{is the container destroyed after that? you are changing
  the environment for a certain bug, right?!} The first step is a
sanity check to assure that the bug can indeed be reproduced. For
example, the following command runs FreeFuzz on the enviroment of the
bug associated with the issue 117033 from \torch.

@@

\Fix{Consider the comments from Saikat, please.}
Initially the script reproduces the bug, then it updates the environment inside the docker container of FreeFuzz to match the enviroment of the bug. Then it proceeds to run the entire testing tool on the enviroment. After the execution completes, the output can be checked for all failures produced by FreeFuzz (saved inside the container) and manually inspected to see if any failure that can reveal the bug in question was generated by the tool. In this case, the failure generated by FreeFuzz could not generate a failure that can reveal this bug since the API "torch.\_dynamo.export" is not supported by FreeFuzz.

@@

\Fix{@Saikat, can you please write 1-2 sentences about each use case here?}

@@

\Fix{Marcelo will write a paragraph}

@@

\section{Walkthrough}

\Fix{}
